Red, Blue, or Purple? 2024’s Battleground States Tell a Story

### 2024-11-04 paper/paper.qmd

# Display the first 5 rows as a table using kable
state_effects_read %>%
  head(5) %>%
  kable(
    col.names = c("State", "Pollster Rating Name", "State Effect"),
    caption = "State Effects",
    booktabs = TRUE
  ) %>%
  kable_styling(latex_options = c("striped", "scale_down", "hold_position"))

@@

@tbl-state_effects illustrates the state effect，The state effects in this Hierarchical Bayesian Model provide adjustments to account for unique voting patterns across different states, enhancing the accuracy of election predictions. For instance, Alabama shows relatively high state effect values, like 55.6 from John Zogby Strategies, suggesting an upward adjustment that aligns with Alabama’s regional voting tendencies. In contrast, Alaska displays lower effect values, such as 45.6 from Alaska Survey Research, indicating a possible regional leaning away from certain candidates.

@@

# Display the first 5 rows as a table using kable
pollster_effects_read %>%
  head(5) %>%
  kable(
    col.names = c("Pollster Rating Name", "Pollster Effect"),
    caption = "Pollster Effects",
    booktabs = TRUE
  ) %>%
  kable_styling(latex_options = c("striped", "scale_down", "hold_position"))

@@

# Display the first 5 rows as a table using kable
candidate_fixed_effect_read %>%
  head(5) %>%
  kable(
    col.names = c("Candidate Name", "Candidate Fixed Effect (gamma_k)"),
    caption = "Candidate Fixed Effects",
    booktabs = TRUE
  ) %>%
  kable_styling(latex_options = c("striped", "scale_down", "hold_position"))

@@

# Save weighted_predictions to an Excel file
write_xlsx(weighted_predictions, path = here("data", "02-analysis_data", "weighted_predictions.xlsx"))

# Optionally, display the first 5 rows as a table using kable
weighted_predictions %>%
  head(5) %>%
  kable(
    col.names = c("State", "Candidate Name", "Weighted Percentage", "Total Weight"),
    caption = "Weighted Predictions by Poll Score and Sample Size",
    booktabs = TRUE
  ) %>%
  kable_styling(latex_options = c("striped", "scale_down", "hold_position"))

@@

5. Adjustment of weighted predictions by accounting for recency $( \theta_{\mathrm{days\_to\_election\_ijk}} )$

@@

# Save weighted predictions to Excel
write_xlsx(weighted_predictions, path = here("data", "02-analysis_data", "weighted_predictions_with_recency.xlsx"))

# Display first 5 rows without extra styling
weighted_predictions %>%
  head(5) %>%
  kable(
    col.names = c("State", "Candidate Name", "Weighted Percentage", "Total Weight"),
    caption = "Weighted Predictions with Recency Adjustment"
  )
  # Avoid using `booktabs` or `latex_options` here to prevent LaTeX conflicts

@@

# Display the calculated adjustment term
#head(data$pollster_reliability_adjustment)

# Save weighted_predictions to an Excel file
#write_xlsx(weighted_predictions, path = here("data", "02-analysis_data", "Pollscore_reliability_adjust.csv"))
```
Pollster reliability represents an adjustment factor that accounts for the credibility and historical accuracy of each pollster’s results. Pollster reliability scores are typically calculated based on a pollster’s past performance, including how closely their predictions align with actual election outcomes. This score reflects the likelihood that a given poll’s results accurately represent voter sentiment. By either increasing or decreasing it based on the reliability score; a higher score would yield a more positive adjustment, while a lower score would lead to a reduction. This adjustment aims to reduce the influence of less reliable polls, thereby improving the model’s overall accuracy by weighting predictions according to the quality of the polling data.

@@

```{r}
#| label: fig-modelresults_map
#| echo: false
#| warning: false
#| message: false
# Load necessary libraries
library(tidyverse)
library(readxl)
library(ggplot2)
library(usmap)  # For easier mapping of U.S. states
library(here)

# Load the weighted predictions data with recency adjustments
predictions <- read_excel(here("data", "02-analysis_data", "weighted_predictions_with_recency.xlsx"))

>>>>

# Display the first 5 rows as a table using kable
state_effects_read %>%
  head(5) %>%
  kable(
    col.names = c("State", "Pollster Rating Name", "State Effect"),
    caption = "State Effects Example",
    booktabs = TRUE
  ) %>%
  kable_styling(latex_options = c("striped", "scale_down", "hold_position"))

@@

@tbl-state_effects illustrates the state effect examples in this Hierarchical Bayesian Model provide adjustments to account for unique voting patterns across different states, enhancing the accuracy of election predictions. For instance, Alabama shows relatively high state effect values, like 55.6 from John Zogby Strategies, suggesting an upward adjustment that aligns with Alabama’s regional voting tendencies. In contrast, Alaska displays lower effect values, such as 45.6 from Alaska Survey Research, indicating a possible regional leaning away from certain candidates.

@@

# Display the first 5 rows as a table using kable
pollster_effects_read %>%
  head(5) %>%
  kable(
    col.names = c("Pollster Rating Name", "Pollster Effect"),
    caption = "Pollster Effects Example",
    booktabs = TRUE
  ) %>%
  kable_styling(latex_options = c("striped", "scale_down", "hold_position"))

@@

# Display the first 5 rows as a table using kable
candidate_fixed_effect_read %>%
  head(5) %>%
  kable(
    col.names = c("Candidate Name", "Candidate Fixed Effect (gamma_k)"),
    caption = "Candidate Fixed Effects Example",
    booktabs = TRUE
  ) %>%
  kable_styling(latex_options = c("striped", "scale_down", "hold_position"))

@@

# Save weighted_predictions to an Excel file
write_csv(weighted_predictions, path = here("data", "02-analysis_data", "weighted_predictions.csv"))

# Optionally, display the first 5 rows as a table using kable
weighted_predictions %>%
  head(5) %>%
  kable(
    col.names = c("State", "Candidate Name", "Weighted Percentage", "Total Weight"),
    caption = "Weighted Predictions by Poll Score and Sample Size Example",
    booktabs = TRUE
  ) %>%
  kable_styling(latex_options = c("striped", "scale_down", "hold_position"))

@@

5. Adjustment of weighted predictions by accounting for recency $( \theta \cdot \mathrm{days\_to\_election}_{ijk} )$

@@

# Save weighted predictions to Excel
write_csv(weighted_predictions, path = here("data", "02-analysis_data", "weighted_predictions_with_recency.csv"))

# Display first 5 rows without extra styling
weighted_predictions %>%
  head(5) %>%
  kable(
    col.names = c("State", "Candidate Name", "Weighted Percentage", "Total Weight"),
    caption = "Weighted Predictions with Recency Adjustment Examples"
  )
  # Avoid using `booktabs` or `latex_options` here to prevent LaTeX conflicts

@@

```
Pollster reliability represents an adjustment factor that accounts for the credibility and historical accuracy of each pollster’s results. Pollster reliability scores are typically calculated based on a pollster’s past performance, including how closely their predictions align with actual election outcomes. This score reflects the likelihood that a given poll’s results accurately represent voter sentiment. By either increasing or decreasing it based on the reliability score; a higher score would yield a more positive adjustment, while a lower score would lead to a reduction. This adjustment aims to reduce the influence of less reliable polls, thereby improving the model’s overall accuracy by weighting predictions according to the quality of the polling data.

@@

```{r}
#| label: fig-modelresults_map
#| echo: false
#| warning: false
#| message: false
#| fig-width: 20
#| fig-height: 8
#| fig.fullwidth: true
# Load necessary libraries
library(tidyverse)
library(readxl)
library(ggplot2)
library(usmap)  # For easier mapping of U.S. states
library(here)

# Load the weighted predictions data with recency adjustments
predictions <- read_excel(here("data", "02-analysis_data", "weighted_predictions_with_recency.csv"))
